### 2021-11-25 input/proposal.tex
wip

%% \begin{definition}[Edge infrastructure]
%%   An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
%%   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
%%   \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
%%   \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
%%     k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
%%   \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
%% \end{definition}

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that the functioning of epidemic propagation is
well-aligned with the objectives of scoped broadcast. More precisely,
it underlines the transitive relevance of messages, thus a \process
can stop \TODO{forwarding messages} as soon as its predicate becomes
unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.
%
We use \NAMEB to efficiently modify the state of each \process
depending on the partitions that exist in the system.

@@

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
  message $\alpha_x$, when $x$ deletes its partition, either every
  \process of this chain eventually deliver $\delta_s$, or a \process
  along the chain detects the blocking of the staleness notification
  $\delta_s$.
\end{lemma}

\begin{proof}
  \TODO{Rework this!} We must prove that every \process that delivered
  a stale $\alpha_X$ eventually delivers a better $\alpha_Y$, or
  delivers a removal notification of $\alpha_X$.
  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
  involving concurrent operations.

@@

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$.
\end{definition}

@@

@@

\begin{proof}
  By design, obvious.
\end{proof}

To provide lazy partitioning, \emph{gateway} \nodes that link
autonomous systems together must acknowledge if there exists a source
in their network.

Must differentiate local from global when they cross the gates.

% \NAME enables indexing the closest replica of each \process without
% flooding the whole network when a new replica appears or disappears.
% Nevertheless, every node must partake in the indexing of each
% content. When the networks accounts for billions of content, this
% raises scalability issues. Inspired by the Internet topology that
% comprises tens of thousands of interconnected autonomous systems
% serving billions of , we want to further
% lock-down traffic by leveraging the edges of networks as barriers, and
% enable on-demand indexing.

>>>>

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that the functioning of epidemic propagation is
well-aligned with the objectives of scoped broadcast. More precisely,
it underlines the transitive relevance of messages, thus a \process
can stop \TODO{forwarding messages} as soon as its predicate becomes
unverified.  We use \NAMEB to efficiently modify the state of each
\process depending on the partitions that exist in the system.

@@

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
  message $\alpha_x$ with $\alpha_x = \min D_z$, when $x$ deletes its
  partition, either every \process of this chain eventually delivers
  $\delta_x$, or a \process along the chain detects the blocking of
  the staleness notification $\delta_s$.
\end{lemma}

\begin{proof}
  Assuming a chain of \processes $[x, x_2, \ldots, y]$ such that
  $\alpha_x \min D$

  Assuming $[x, x_2, \ldots, x_k, y, y_1, y_2, \ldots, y_\ell, z]$,

@@

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$. A \emph{gateway} $g$ is a
  \process with at least one link towards another network: $\langle g,
  \_ \rangle \in \mathcal{E}$.
\end{definition}

@@

To enable LDCP in an Edge infrastructure, we use the property provided
by DCP in an autonomous system to all its \processes and among others,
to its gateways.

@@

\begin{proof}
  By design, \TODO{obvious}.
\end{proof}

The gateways become responsible for the flooding or the stopping of
notifications foreign to their respective network. They must
differentiate between local and global notifications. Local
notifications provide both \begin{inparaenum}[(i)]
\item local source existence, and
\item closest local source in the network
\end{inparaenum}; while global notifications only improve on closest global sources,
\ie it does not need to propagate when the foreign source is farther
than the local one.

\begin{definition}[\underline{B}roadcasting of \underline{u}ninterested (BU)]
  \TODO{meow}
\end{definition}

\TODO{Blocking condition local global remains.}
